### 2016-04-03 writing/tex/sections/coincidence.tex
last writing update, writing in another place, may yet move

    \begin{enumerate}
        \item \(R_1 \triangle R_2 = \{(a,b)\}\)
        \item \(\pi \preceq \addp{\sigma}{(a,b)}\)
    \end{enumerate}
\end{proposition}
\begin{proof}
\end{proof}

>>>>

    \begin{enumerate}
        \item \(R_1 \triangle R_2 = \{(a,b)\}\)
        \item \(\pi \preceq \addp{\sigma}{(a,b)}\)\label{prop:dom1:cont}
    \end{enumerate}
\end{proposition}
In order to prove this proposition we must first make the following note.

\begin{note}
    \label{not:downcmesh}
    Let \(R^\prime \subseteq R\). Then any occurence of \((\tau, R)\) in a permutation
    is an occurence of \((\tau,R^\prime)\).
\end{note}
\begin{proof}
    Assume without meaningful loss of generality that \(R^\prime\) is a proper
    subset of \(R\).

    Consider an occurence of \((\tau, R)\) in a permutation \(\sigma\), obviously
    this corresponds to an occurrence of \(\tau\) in \(\sigma\). Now consider
    the mesh sets \(R\) and \(R^\prime\), since \(R^\prime \subseteq R\) then
    there are more restrictions on where points are in an occurrence of \((\tau,R)\).
    Namely, for every shaded box in \(R\) the corresponding region in \(\sigma\)
    must contain no points, since \(R^\prime\) has less shading than \(R\) there
    exists a region in the occurence of \((\tau,R)\) in \(\sigma\) that is
    now devoid of restrictions. However, by removing restrictions we cannot
    make an occurence become not an occurence, and therefore the same occurrence
    of \(\tau \) in \(\sigma\) is now an occurence of \((\tau, R^\prime)\).

\end{proof}
\begin{proof}[Proof of Proposition~\ref{prop:dom1}]

    We need to prove that \(\av{\{\pi,m_1\}} = \av{\{\pi,m_2\}}\), or equivalently
    \(\mathfrak{S}\setminus \av{\{\pi,m_1\}} = \mathfrak{S}\setminus \av{\{\pi,m_1\}}\).

    Assume without meaningful loss of generality that \(R_2 = R_1 \cup \{(a,b)\}\).

    Consider a permutation \(\omega\) that contains an occurrence of \(m_2\)
    by Note~\ref{not:downcmesh} any of these occurrences is also an occurence
    of \(m_1\). This proves that every occurence of \(m_2\) is also an
    occurence of \(m_1\) and \(\mathfrak{S}\setminus \av{\{\pi,m_2\}}
    \subseteq \mathfrak{S}\setminus \av{\{\pi,m_1\}}\).

    Now we consider a permutation \(\omega^\prime\) containing an occurence of
    \(m_1\). Consider placing a point in the region corresponding to the box
    \((a,b)\), regardless of where in this region we place the point by
    condition~\ref{prop:dom1:cont} of the Proposition we create an occurrence
    of \(\pi\), therefore there can be no points in this region, which
    could have been represented in the mesh set \(R_1\) by adding the box
    \((a,b)\), and therefore every occurrence of \(m_1\) is in fact an
    occurrence of \(m_2\).\qedhere

\end{proof}
